FTLR proof cases

### 2018-06-12 fully-abstract-comp/ftlr-proof-cases.tex
Updated semantics of scall, so it matches what the implementation does when one of the registers is the temp register.
typo

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\update{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\update{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
In order to do this, we first, we prove that one of the following holds:
\lau{TODO: add $\neq$ failed to the cases that are not failed.}
\begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
    \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{\aaddr_\stk,\eaddr_\stk}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
      \lau{TODO: Need to have an explicit $\offpc$.}
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.
\\\\
In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
steps, so both directions of $\lro$ are trivially satisfied.
\\\\
In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.
\\\\
\lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.}
In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump.
  If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.}
and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.}
as this will cause the execution to fail.
We need to let the target execution catch up.
That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
\[
\Phi_T'' = \Phi_T
\begin{array}[t]{l}
  \update{\mem.\aaddr_\stk}{42} \\
  \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
  \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
  \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
  \updReg{\rtmp{1}}{0}\\
  \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
  \updReg{\pcreg}{c_1'}\\
  \updReg{\rdata}{c_2'}
\end{array}
\]
where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
\[
  \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
\]
By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrr(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrv$ we get
$\npair[n'-1]{\stpair[.]{c_2}{c_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
and w.l.o.g.\

>>>>

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrrg{\trust}(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\update{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\update{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
In order to do this, we first, we prove that one of the following holds:
\lau{TODO: add $\neq$ failed to the cases that are not failed.}
\begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
    \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{\aaddr_\stk,\eaddr_\stk}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
      \lau{TODO: Need to have an explicit $\offpc$.}
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
either assume that the target configuration terminates or that the source
configuration terminates, but in either case it leads to a contradiction with
the failing configuration.
\\\\
In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
steps, so both directions of $\lro$ are trivially satisfied.
\\\\
In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to get
\[
  \npair[n'-1]{(((\perm,\lin),\baddr,\eaddr,\aaddr+1),((\perm,\lin),\baddr,\eaddr,\aaddr+1))} \in \lre(W)
\]
This is possible by using the initial assumptions along with Lemma \ref{lem:downwards-closed}.
By Lemma~\ref{lem:downwards-closed}, we know $\memSat[n'-1]{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$.
By Lemma~\ref{lem:downwards-closed} and the fact that integers are always safe,
we know $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$.
This allows us to conclude
\[
  \npair[n'-1]{(\Phi_S',\Phi_T')} \in \lro
\]
as desired.
\\\\
\lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.}
In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump.
  If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.}
and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.}.
as this will cause the execution to fail.
We need to let the target execution catch up.
That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
\[
\Phi_T'' = \Phi_T
\begin{array}[t]{l}
  \update{\mem.\aaddr_\stk}{42} \\
  \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
  \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
  \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
  \updReg{\rtmp{1}}{0}\\
  \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
  \updReg{\pcreg}{c_1'}\\
  \updReg{\rdata}{c_2'}
\end{array}
\]
where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
\[
  \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
\]
By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrr(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrv$ we get
$\npair[n'-1]{\stpair[.]{c_2}{c_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
and w.l.o.g.\
